What Variables Impact Wicket Production in the IPL

### 2024-12-13 paper/paper.qmd
added toc

---
title: "What Variables Impact Wicket Production in the IPL"
subtitle: "Wicket can come in bunches in the IPL"
author: 
  - Siddharth Gowda
thanks: "Code and data are available at: [https://github.com/siddharthgowda/ipl_wicket_analysis](https://github.com/siddharthgowda/ipl_wicket_analysis)."
date: today
date-format: long
abstract: "The paper analyzes what variables are the best predictors of wickets in the Indian Permier League (IPL). The current over, the bowling style, batting hand, and the number of wickets in the previous over impact the probability of a wicket occuring. Moreover, the number of wickets in the previous over is the greatest predictor of wickets occuring. These findings can be used by IPL teams when attempting large comebacks or when trying to prevent comebacks."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "What Variables Impact Wicket Production in the IPL"
subtitle: "Wicket can come in bunches in the IPL"
author: 
  - Siddharth Gowda
thanks: "Code and data are available at: [https://github.com/siddharthgowda/ipl_wicket_analysis](https://github.com/siddharthgowda/ipl_wicket_analysis)."
date: today
date-format: long
abstract: "The paper analyzes what variables are the best predictors of wickets in the Indian Permier League (IPL). The current over, the bowling style, batting hand, and the number of wickets in the previous over impact the probability of a wicket occuring. Moreover, the number of wickets in the previous over is the greatest predictor of wickets occuring. These findings can be used by IPL teams when attempting large comebacks or when trying to prevent comebacks."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---
